Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-04 supplement/06_bat_data.Rmd
minor edits

Some preparation is required. First, the function requires columns `x`, `y`,
`time`, and `id`, which we assign using the `data.table` syntax. The `time` column is already present, but the other columns need to be renamed to lower case.
Then we subset the data to only work with positions where the individual had a residence time of more than 5 minutes.

@@

# exclude roost
patch_summary <- patch_summary[x_median > 254000, ]

@@

patch_summary[, night := 1 + c(0, cumsum(diff(hour) > 12)), by = "id"]

# get total foraging time
foraging_proportion <- patch_summary[, list(
  time_total_forage = (max(time_end) - min(time_start)) / 60,
  time_forage_site = sum(duration / 60)
),
by = c("id", "night")
]

>>>>

Some preparation is required. First, the function requires columns `x`, `y`,
`time`, and `id`, which we assign using the `data.table` syntax. The `time` column is already present, but the other columns need to be renamed to lower case.

@@

@@

# get total foraging time
foraging_proportion <- patch_summary[, list(
  time_total_forage = (max(time_end) - min(time_start)) / 60,
  time_forage_site = sum(duration / 60)
),
by = c("id", "night_mean")
]
